\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-07-22 doc/sw-system-referee-response.txt

Page 10, maybe the title of subsection 4.5 : "Practicalities" should
be changed for a more specific title here.

    Done. We've gone with "Application to the CFHTLS Classifications".

Page 11, Figure 5, the figure is interesting but it should be better
highlighted with clearer color contrasts, for the histograms and for
the circles.

    TO DO! Edit SWAP to make red and blue points bigger, red and blue
    trajectories thicker and less alpha'd, red and blue histograms
    in the foreground with alpha=1. Issued as #219

@@

Page 18, subsection 6.3, 1st paragraph, line 7, there is a 'typo' :
"quantitively".

    Fixed.

The authors should add a discussion about the complexity of computing
of a selection function in the case of visual inspection compared to
the automated methods.

    We are happy to provide a new paragraph on this topic at the end
    of Section 5.1 (Results: Sample Properties). In short, we believe
    that computing a selection function based on the quantitative,
    probabilistic classification labels produced by the Space Warps
    system should be no more difficult or complex than doing so based
    on the outputs of a machine classifier, which would correspond
    exactly in character.

### 2015-07-22 doc/sw-system.tex
Added selection function paragraph: #216 now all done bar the plots from @cpadavis

>>>>

Finally, it is worth noting the implications of the results in this
section for future studies of samples of lenses (and lens candidates)
discovered through visual inspection at \SW. The ROC curve analysis we
have carried out should be very familiar to those working in machine
classification, and in fact is identical to that which would be
performed on the classifications made by a new automated method.
Supervised machine learning methods and the \SW system as described
here both require a training set, and both return quantitative,
probabilistic classifications (consisting of a label and some measure
of confidence in that label) that can be used in further analysis. A
good example of where such quantitification is important is in the
derivation of the selection function for a given sample. While such a
derivation is beyond the scope of this work, it is sufficient to note
that from the point of view of an astronomer seeking to derive a
selection function, {\it the labels produced by \SW and those produced
by a machine learning method can be treated equivalently}: that is, we
have succeeded in elevating visual inspection to a quantitative
science. Indeed, the discussion of completeness given above is all in
terms of recovery of a large set of simulated lenses, just as it would
be in the case of an automated method---and in both cases, the
limiting factor is the realism of the training set. In \PaperTwo we
investigate this further by assessing the performance of the \SW
system against the (small) set of real lens candidates known to lie in
the field; for now, we note that the training set used in this work
constitutes a valid sample of objects for any alternative machine
learning lens detection method to be tested against. In future, we may
well find it necessary to employ a larger training set, to enable the
selection efficiency to be characterised as a function of multiple
observables. This should not be a problem, since in the current work
the small training set we used was classified around 20 times more
than  was the test set: we could have defined a larger training set,
and collected  many fewer classifications per training image.
